### 2016-02-18 paper.tex
Add some turbine geometry details
Add some commentary on existing data

A selection of measured performance data in the literature and its usage in
numerical model validation is presented in Table~\ref{tab:validation-data}.

@@

@@

>>>>

A selection of measured performance data in the literature and its usage in
numerical model validation is presented in Table~\ref{tab:validation-data}.
Turbine diameter Reynolds numbers spanned from small laboratory scale ($Re_D
\sim 10^5$) all the way to full scale ($Re_D \sim 10^7$). Individual blade
forces were only measured in two of the experiments---Strickland \emph{et al.}
\cite{Strickland1981} and Laneville and Vitecoq \cite{Laneville1986}. There has
been nearly equal attention given to the eggbeater-shaped Darrieus rotor and the
straight-bladed H-rotor. The two additional rotors studied were the large scale
tapered H-rotor VAWT 850 \cite{Mays1990} and the helical Quiet Revolution QR5
measured by Penna \cite{Penna2008}, the exact geometry for which is unknown.

@@

In general, there have been more experiments done with rotors of low $c/R$,
which makes them easier to model, since unsteady dynamic effects are less
influential on the overall performance \cite{Strickland1981}. This is apparent
when examining the effectiveness of numerical models that rely on static foil
coefficient input data, e.g., streamtube and vortex models, which seem to be
most applicable for $c/R \leq 0.1$.

@@

The rotor was 1.075 m in diameter and 0.8067 m tall, with blade chords that
taper from 0.04 m at the tips to 0.067 m at the roots, or half-span. Mean
chord-to-radius ratio $c/R$ was 0.1, which is approximately at the threshold
between high and low solidity \cite{Strickland1981,Fiedler2009}. This rotor
geometry presents a unique validation case not yet seen in the literature,
similar in concept to the VAWT 850 \cite{Mays1990} with its tapered blades, but
with a moderately high $c/R$ to more accurately represent typical MHK rotors,
which presents a challenge for numerical modeling.
